Exploration

### 2018-03-09 exploration.Rmd
made NDD consistent in simulation and theoretical

  #---- generate data
  ## survival
  E_surv <- antilogit(size.mx[,1:n_sz] %*% p$s_z + c(X_s[i,] %*% p$s_x))
  d[[i]]$surv <- rbinom(n_i[i], 1, E_surv)
  ## growth
  E_grow <- size.mx[,1:n_gz] %*% p$g_z + c(X_g[i,] %*% p$g_x)
  d[[i]]$sizeNext <- rnorm(n_i[i], E_grow, p$g_sig)
  d[[i]]$sizeNext <- ifelse(d[[i]]$surv, d[[i]]$sizeNext, NA)
  ## flowering 
  E_fl <- antilogit(size.mx[,1:n_flz] %*% p$fl_z + c(X_fl[i,] %*% p$fl_x))
  d[[i]]$fl <- rbinom(n_i[i], 1, E_fl)
  ## seed production
  E_seed <- d[[i]]$fl * 
    exp(size.mx[,1:n_seedz] %*% p$seed_z + c(X_seed[i,] %*% p$seed_x))
  d[[i]]$seed <- rpois(n_i[i], E_seed)
  # d[[i]]$fl <- ifelse(d[[i]]$surv, d[[i]]$fl, NA)
  d[[i]]$seed <- ifelse(d[[i]]$fl==1, d[[i]]$seed, NA)
  nSd[i] <- sum(d[[i]]$seed, na.rm=T)
  ## seed bank: native
  B_1[i] <- B[i] * p$s_SB * (1 - p$rcr_SB) + 
    nSd[i] * (1 - p$p_emig) * (1 - p$rcr_dir) * p$s_SB
  ## recruits: native
  p_est.i[i] <- ifelse(p$NDD, sum(d[[i]]$surv==1)/nSd[i], p$p_est)
  rcr.n <- round(nSd[i] * (1 - p$p_emig) * p$rcr_dir * p_est.i[i] +
                   B[i] * p$rcr_SB * p_est.i[i]) # ≥ 2 for IPMpack sd(rcr_z')
  if(rcr.n > 0) {
    rcr.i <- (1:rcr.n) + n_i[i]
    d[[i]][rcr.i,] <- NA
    d[[i]]$sizeNext[rcr.i] <- rnorm(rcr.n, p$rcr_z[1], p$rcr_z[2])
  }
  ## emigrants
  sdd[,,3,i] <- nSd[i] * p$p_emig * sdd[,,1,i]
}
# dispersal
for(i in 1:n.cell) {
  sdd.i <- env.df$id[i] # full rectangle grid id for SDD indexes

@@

  #---- generate data: add immigrants
  # total immigrants
  D[i] <- sum(sdd[,,3,][sdd.j])
  # seed bank: immigrants
  B_1[i] <- B_1[i] + D[i] * (1 - p$rcr_dir) * p$s_SB
  # recruits: immigrants
  rcr.imm <- round(D[i] * p$rcr_dir * p_est.i[i])
  if(rcr.imm > 0) {
    rcr.i <- (1:rcr.imm) + nrow(d[[i]])
    d[[i]][rcr.i,] <- NA
    d[[i]]$sizeNext[rcr.i] <- rnorm(rcr.imm, p$rcr_z[1], p$rcr_z[2])
  }
}
# density dependence
if(p$NDD) {
  lam.t <- p_est.t <- matrix(nrow=tmax-1, ncol=n.cell)
  for(i in 1:n.cell) {
    Nt[,,i,1] <- rpois((n+1)*(n+1), n_i)
    for(k in 1:(tmax-1)) {
      F.t <- Fs[,,i]
      # set p_est to density dependent value if that is < p$p_est
      p_est.t[k,i] <- min(195/(sum(F.t[z.i,] * Nt[z.i,,i,k])/p$p_est), p$p_est)
      # F.s[,,i] was already multiplied by p$p_est, so divide by that first
      F.t[z.i,] <- F.t[z.i,]/p$p_est * p_est.t[k,i]
      IPM.t <- Ps[,,i] + F.t
      Nt[,,i,k+1] <- IPM.t %*% Nt[,,i,k]
      lam.t[k,i] <- Re(eigen(IPM.t)$values[1])
    }
  }
}
IPMs <- Ps + Fs
lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
lam.df %<>% 
  add_column(nSd=nSd, B0=B, B1=B_1, D=D, N=map_dbl(d, ~sum(!is.na(.$sizeNext))),
             N.surv=map_dbl(d, ~sum(.$surv, na.rm=T)),
             N.rcr=map_dbl(d, ~sum(is.na(.$size)))) %>%
  mutate(nSdStay=nSd*(1-p$p_emig), nSdLeave=nSd*p$p_emig) %>%
  add_column(Ntmax=apply(Nt[,,,tmax],3,sum), lam.tmax=lam.t[tmax-1,])

>>>>

  #---- generate data
  ## survival
  E_surv <- antilogit(size.mx[,1:n_sz] %*% p$s_z + c(X_s[i,] %*% p$s_x))
  d[[i]]$surv <- rbinom(n_i[i], 1, E_surv)
  ## growth
  E_grow <- size.mx[,1:n_gz] %*% p$g_z + c(X_g[i,] %*% p$g_x)
  d[[i]]$sizeNext <- rnorm(n_i[i], E_grow, p$g_sig)
  d[[i]]$sizeNext <- ifelse(d[[i]]$surv, d[[i]]$sizeNext, NA)
  ## flowering 
  E_fl <- antilogit(size.mx[,1:n_flz] %*% p$fl_z + c(X_fl[i,] %*% p$fl_x))
  d[[i]]$fl <- rbinom(n_i[i], 1, E_fl)
  ## seed production
  E_seed <- d[[i]]$fl * 
    exp(size.mx[,1:n_seedz] %*% p$seed_z + c(X_seed[i,] %*% p$seed_x))
  d[[i]]$seed <- rpois(n_i[i], E_seed)
  # d[[i]]$fl <- ifelse(d[[i]]$surv, d[[i]]$fl, NA)
  d[[i]]$seed <- ifelse(d[[i]]$fl==1, d[[i]]$seed, NA)
  nSd[i] <- sum(d[[i]]$seed, na.rm=T)
  ## seed bank: native
  B_1[i] <- B[i] * p$s_SB * (1 - p$rcr_SB) + 
    nSd[i] * (1 - p$p_emig) * (1 - p$rcr_dir) * p$s_SB
  ## recruits: native
  p_est.i[i] <- ifelse(p$NDD, min(150/nSd[i], p$p_est), p$p_est)
  rcr.n <- round(nSd[i] * (1 - p$p_emig) * p$rcr_dir * p_est.i[i] +
                   B[i] * p$rcr_SB * p_est.i[i]) # ≥ 2 for IPMpack sd(rcr_z')
  if(rcr.n > 0) {
    rcr.i <- (1:rcr.n) + n_i[i]
    d[[i]][rcr.i,] <- NA
    d[[i]]$sizeNext[rcr.i] <- rnorm(rcr.n, p$rcr_z[1], p$rcr_z[2])
  }
  ## emigrants
  sdd[,,3,i] <- nSd[i] * p$p_emig * sdd[,,1,i]
}
# dispersal
for(i in 1:n.cell) {
  sdd.i <- env.df$id[i] # full rectangle grid id for SDD indexes

@@

  #---- generate data: add immigrants
  # total immigrants
  D[i] <- sum(sdd[,,3,][sdd.j])
  # seed bank: immigrants
  B_1[i] <- B_1[i] + D[i] * (1 - p$rcr_dir) * p$s_SB
  # recruits: immigrants
  rcr.imm <- round(D[i] * p$rcr_dir * p_est.i[i])
  if(rcr.imm > 0) {
    rcr.i <- (1:rcr.imm) + nrow(d[[i]])
    d[[i]][rcr.i,] <- NA
    d[[i]]$sizeNext[rcr.i] <- rnorm(rcr.imm, p$rcr_z[1], p$rcr_z[2])
  }
}
# density dependence
if(p$NDD) {
  lam.t <- p_est.t <- matrix(nrow=tmax-1, ncol=n.cell)
  for(i in 1:n.cell) {
    Nt[,,i,1] <- rpois((n+1)*(n+1), n_i)
    for(k in 1:(tmax-1)) {
      F.t <- Fs[,,i]
      # set p_est to density dependent value if that is < p$p_est
      p_est.t[k,i] <- min(150/(sum(F.t[z.i,] * Nt[z.i,,i,k])/p$p_est), p$p_est)
      # F.s[,,i] was already multiplied by p$p_est, so divide by that first
      F.t[z.i,] <- F.t[z.i,]/p$p_est * p_est.t[k,i]
      IPM.t <- Ps[,,i] + F.t
      Nt[,,i,k+1] <- IPM.t %*% Nt[,,i,k]
      lam.t[k,i] <- Re(eigen(IPM.t)$values[1])
    }
  }
}
IPMs <- Ps + Fs
lam.df <- env.df
lam.df$lambda <- apply(IPMs, 3, function(x) Re(eigen(x)$values[1]))
lam.df %<>% 
  add_column(nSd=nSd, B0=B, B1=B_1, D=D, N=map_dbl(d, ~sum(!is.na(.$sizeNext))),
             N.surv=map_dbl(d, ~sum(.$surv, na.rm=T)),
             N.rcr=map_dbl(d, ~sum(is.na(.$size)))) %>%
  mutate(nSdStay=nSd*(1-p$p_emig), nSdLeave=nSd*p$p_emig) %>%
  add_column(Ntmax=apply(Nt[,,,tmax],3,sum), lam.tmax=lam.t[tmax-1,])
